\documentclass{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
%
\title{Year 6}%
\author{Zhenglin}%
\date{\today}%
%
\begin{document}%
\normalsize%
\maketitle%
\section*{3.1 Using letters to represent numbers (1)}%
\begin{enumerate}%
\item%
$b+b+b+b\times b$ can be simply written as $\rule{2cm}{0.15mm}$%
\item%
In a triangle, if $\angle 1=a^{\circ}$ and $\angle 2=b^{\circ}$, then $\angle 3=$ $\rule{2cm}{0.15mm}$.%
\item%
In an isosceles triangle, if the base angle is $a^{\circ}$, the degree of the vertex angle is $\rule{2cm}{0.15mm}$%
\item%
When the sum of three consecutive even number is $a$, then the number in the middle is $\rule{2cm}{0.15mm}$, the least number is $\rule{2cm}{0.15mm}$ and the gratest number is $\rule{2cm}{0.15mm}$%
\end{enumerate}

%
\section*{3.2 Using letters to represent numbers (2)}%
\begin{enumerate}%
\item%
Use expressions with letters to represent the relations between quantities.%
\begin{itemize}%
\item%
The quotient of $5$ divided by $x$ plus $n$ is $\rule{2cm}{0.15mm}$%
\item%
$320$ is substracted by $12$ times $m$: $\rule{2cm}{0.15mm}$%
\end{itemize}%
\item%
Use expressions with letters to represent the quantities below%
\begin{itemize}%
\item%
A car has travelled $t$ hours at the speed of 85 km per hour. It has travelled $\rule{2cm}{0.15mm}$ $km$ in total%
\item%
A shirt cost $a$ pounds, and a pair of trousers costs $b$ pounds.. The total cost of buying 3 sets of these clothes is $\rule{2cm}{0.15mm}$ pounds%
\end{itemize}%
\item%
Look at each number sequence carefully and complete its $5^{th}$, $6^{th}$, and $n^{th}$ terms.%
\begin{itemize}%
\item%
0, 5, 10, 15, $\rule{2cm}{0.15mm}$, $\rule{2cm}{0.15mm}$, ... , $\rule{2cm}{0.15mm}$%
\item%
13, 23, 33, 43, $\rule{2cm}{0.15mm}$, $\rule{2cm}{0.15mm}$, ..., $\rule{2cm}{0.15mm}$%
\end{itemize}%
\end{enumerate}

%
\section*{3.3 Simplification and evaluation (1)}%
\begin{enumerate}%
\item%
Simplify the following expressions.%
\begin{itemize}%
\item%
$36s-15t-24s+35t=$ $\rule{2cm}{0.15mm}$%
\item%
$48x+75y-18x-6x$ $\rule{2cm}{0.15mm}$%
\end{itemize}%
\item%
Fill in the blank%
\begin{itemize}%
\item%
Joe has $x$ pencils. Roy has 3 more pencils than Joe. They have $\rule{2cm}{0.15mm}$ pencils altogether%
\item%
Each pack of flour weights 10 kg. Each pack of rice weights $x$ kg. $y$ packs of flour and 5 packs of rice weight $\rule{2cm}{0.15mm}$ kg in total%
\item%
Don, Evans and Frank each bought 4 pens at $a$ pounds each. They paid $\rule{2cm}{0.15mm}$ pounds in total for the pens. They also each bought $b$ exercise books. Each book costs 2 pounds. They paid $\rule{2cm}{0.15mm}$ pounds in total for the books.%
\end{itemize}%
\item%
Short answer questions%
\begin{itemize}%
\item%
\pounds10 can buy $3a$ kg of a fruit. Accordingly, Fiona bought $9.6a$ kg of the fruit with \pounds50. How much change did she get?%
\item%
It took Joan $m$ hours to make 21 paper flowers. It took Marry 2 hours to make $n$ paper flowers. How many paper flowers did each of them make on average? How many paper flowers did both of them make every hour, on average?%
\item%
The dividend is 6 times the divisor. If the divisor is $x$, what is the sum of the dividend, divisor, and quotient?%
\end{itemize}%
\item%
The length and width of a rectangle are $a$ cm and $b$ cm respectively, and $a>b$. The side length of a square equals the difference between the two sides of the rectangle. What is the sum of their perimeters?%
\end{enumerate}

%
\section*{3.4 Simplification and evaluation (2)}%
\begin{enumerate}%
\item%
To repair a section of a road, the repair team repaired $c$ m of the road every day for the first 6 days, and there were $s$ m left.%
\begin{itemize}%
\item%
Use an expression to express the length of the road section: $\rule{2cm}{0.15mm}$%
\end{itemize}%
\item%
Simplify first and then evaluate.%
\begin{itemize}%
\item%
When $m=4$ and $n=1.8$, find the value of $15m+5m-18n-12n$. $\rule{2cm}{0.15mm}$%
\end{itemize}%
\item%
A farm has cultivated sycamores and cedars. They are each in $x$ rows. Sycamores are in rows of 12 and cedars are in rows of 14 across.%
\begin{itemize}%
\item%
How many sycamores and cedars has the farm clutivated in total?%
\item%
When $x=20$, how many sycamores and cedars are there on the farm?%
\end{itemize}%
\item%
There are $a$ pupils in a school\'s track and field team. The number of pupils in the hockey team is 4 fewer than twice the number in the track and field team.%
\begin{itemize}%
\item%
Use an expression with letters to represent the total number of pupils in the two teams%
\item%
When $a=24$, how many pupils are there in the two teams?%
\end{itemize}%
\end{enumerate}

%
\section*{3.5 Simple equations (1)}%
\begin{enumerate}%
\item%
True or False%
\begin{itemize}%
\item%
An expression with variables is an equation.%
\item%
$9-3x$ is not an equation.%
\end{itemize}%
\end{enumerate}

%
\section*{3.6 Simple equations (2)}%
\begin{enumerate}%
\item%
Emily was given \pounds30 in \pounds2 coins and \pounds5 notes. Let $x$ be the number of \pounds2 coins and $y$ be the number of \pounds5 nodes.%
\begin{itemize}%
\item%
Establish an equation with $x$ and $y$%
\item%
List all the possible combinations of $x$ and $y$ that satisfy the equation. (Note: $x$ and $y$ must be positive numbers)%
\end{itemize}%
\item%
A department store received 324 pairs of sports shoes packed in boxes of the same size. If 2 boxes contain 72 pairs of shoes, how many boxes did the store received?%
\end{enumerate}

%
\section*{3.7 Simple equations (3)}%
\begin{enumerate}%
\item%
Write the equation first and then find the solution%
\begin{itemize}%
\item%
The sum of 4 times $x$ and 3.2 is 9.8. Find $x$.%
\end{itemize}%
\item%
Solve the equation: $7.8-x\div3=2.2$%
\end{enumerate}

%
\section*{3.8 Using equations to solve problems (1)}%
\begin{enumerate}%
\item%
Write equations and then solve the application problems.%
\begin{itemize}%
\item%
The area of a rectangle is 36 cm\textsuperscript{2} . The length is 8 cm. What is the width of the rectangle?%
\end{itemize}%
\item%
Julie bought 1 bath towel and 4 hand towels for \pounds20. Given that the price of the bath towel was \pounds6, how much did each hand towel cost?%
\end{enumerate}

%
\end{document}